Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
Add mkl as author, commented
adding supplyment phrase.

\authorinfo{Simon HENGEL}
           {}
           {sol@typeful.net}
\authorinfo{Kazuhiko YAMAMOTO}
           {IIJ Innovation Institute Inc.}
           {kazu@iij.ad.jp}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

We think that some evidence is useful as user documentation.
But there is also evidence, that is not
useful as user documentation.  E.g. that a particular \texttt{Monoid}
instance is a monoid in the mathematical sense is self-evident.

\begin{quote}
    kazu: Monoid is already described in Introduction. Why is this
    repeated? And ``code documentation'' is aslo already dicussed in
    Introduction. I think we can use ``code documentation'' here.

    sol: We reuse Monoid here, but we make a different point.  So this
    still adds something, and I think we need it.
\end{quote}

>>>>

\authorinfo{Simon HENGEL}
           {}
           {sol@typeful.net}
%\authorinfo{Markus KLINIK}
%           {Elektrobit Automotive GmbH}
%           {markus.klinik@elektrobit.com}
\authorinfo{Kazuhiko YAMAMOTO}
           {IIJ Innovation Institute Inc.}
           {kazu@iij.ad.jp}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:introduction}

@@

As we discussed in Section~\ref{sec:introduction},
We think that some evidence is useful as user documentation.
But there is also evidence, that is not
useful as user documentation.  E.g. that a particular \texttt{Monoid}
instance is a monoid in the mathematical sense is self-evident.
